### 2018-12-05 README.Rmd
Add description of link construction
Put the "How to" informations for Colin & Maud

The goal of fishcom is to ...

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

>>>>

[![Build Status](https://travis-ci.org/alaindanet/fishcom.svg?branch=master)](https://travis-ci.org/alaindanet/fishcom)

The goal of fishcom is to get all the informations concerning the ECOSTAB postdoc
project in one place including reproducible code, notes, eventually data and
manuscripts.

## How to

### Get the repository

You can clone the repository with [git](https://git-scm.com/) by pasting in your terminal:

```
git clone https://github.com/alaindanet/fishcom.git dir_name_to_be_created
```
OR

just download the repository: [alaindanet/fishcom](https://github.com/alaindanet/fishcom/archive/master.zip)

### Open it in Rstudio

If you have [Rstudio](https://www.rstudio.com/) installed on your computer, just open `fishcom.Rproj` with
Rstudio.

## Information

My notes are available in the introductory vignette `vignettes/intro.html`
